---
title: "Pachwork - a package laying out multiple ggplots"
author: "Yingjie"
date: "5/14/2020"
output: 
  html_document:
    theme: united
    toc: true
    toc_float:
      collapsed: false ## true
editor_options: 
  chunk_output_type: inline
---


toc: true     # table of content true
toc_depth: 3  # upto three depths of headings (specified by #, ## and ###)
number_sections: true  ## if you want number sections at each table header
theme: united # many options for theme, this one is my favorite.
highlight: tango  # specifies the syntax highlighting style
css: my.css   # you can add your custom css, should be in same folder
    
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

# hide message: message = FALSE
# hide warning: warning = FALSE
# hide all : include = FALSE
# hide results : results = "hide" or results = FALSE
 
```


# Packages
```{r}
if(!require(devtools)) install.packages("devtools")
# devtools::install_github("thomasp85/patchwork")

library(ggplot2)
library(patchwork)
theme_set(
  theme_bw() +
    theme(legend.position = "top")
)
```



# Plots
```{r}
# 0. Define custom color palette and prepare the data
my3cols <- c("#E7B800", "#2E9FDF", "#FC4E07")
ToothGrowth$dose <- as.factor(ToothGrowth$dose)

# 1. Create a box plot (bp)
p <- ggplot(ToothGrowth, aes(x = dose, y = len))
(bxp <- p + geom_boxplot(aes(color = dose)) +
  scale_color_manual(values = my3cols))

# 2. Create a dot plot (dp)
(dp <- p + geom_dotplot(aes(color = dose, fill = dose), 
                       binaxis='y', stackdir='center') +
  scale_color_manual(values = my3cols) + 
  scale_fill_manual(values = my3cols))

# 3. Create a line plot
(lp <- ggplot(economics, aes(x = date, y = psavert)) + 
  geom_line(color = "#E46726")) 

# 4. Density plot
(dens <- ggplot(iris, aes(Sepal.Length)) +
  geom_density(aes(color = Species)) +
  scale_color_manual(values = my3cols))
```


## Horizontal layouts
```{r}
bxp + dens
```


## Vertical layouts
```{r}
bxp + dens + plot_layout(ncol = 1)

```


## Specify the dimensions of each plot
### Change height of each subplot
```{r}
bxp + dens + plot_layout(ncol = 1, heights = c(1, 3))
```


### Change width of each subplot
```{r}
bxp + dens + plot_layout(ncol = 2, width = c(1, 2))
```

### Add space between plots
```{r}
bxp + plot_spacer() + dens

```



## Nested layouts
  You can make nested plots layout by wrapping part of the plots in parentheses - in these cases the layout is scoped to the different nesting levels.
```{r}
lp + {                    ## as a sigle row
  dens + {                ## dense plot and others in a 2nd row
    bxp +
    dp +
    plot_layout(ncol = 1) ## bxp and dp in one col
  }
} +
  plot_layout(ncol = 1)
```


## Advanced features
  patchwork provides some other operators that might be of interest: - (not a subtract, but a hyphen) will behave like + but put the left and right side in the same nesting level (as opposed to putting the right side into the left sides nesting level).
```{r}
bxp + dp - lp  ## width at 1, 1, 2
bxp + dp - lp + plot_layout(ncol = 1) ## bxp + dens and lp is on the same level
```

Often you are interested in just putting plots besides or on top of each other. patchwork provides both | and / for horizontal and vertical layouts respectively. They can of course be combined for a very readable layout syntax
```{r}
(bxp | lp | dp) / dens

(bxp | lp ) / (dp | dens)

```

### Operators for theme
There are two additional operators that are used for a slightly different purpose, namely to reduce code repetition. Consider the case where you want to change the theme for all plots in an assemble.

Instead of modifying all plots individually you can use & or * to add elements to all subplots. The two differ in that * will *only* affect the plots on the current nesting level:
```{r}
(bxp + (dp + dens) + lp + plot_layout(ncol = 1)) * theme_gray()

```


whereas & will recurse into nested levels:
```{r}
(bxp + (dp + dens) + lp + plot_layout(ncol = 1)) & theme_gray()
```


# Ref
https://www.datanovia.com/en/blog/ggplot-multiple-plots-made-ridiculuous-simple-using-patchwork-r-package/
